Solution-aware vs global ReLU selection: \\ partial MILP strikes back for DNN verification

### 2025-04-17 ATVA 2025/proofsb.tex
update

\begin{figure}[b!]
	\hspace*{-0.8cm}
	\includegraphics[scale=0.55]{CNN-B-ADV_layer7_comparison_image85_min.png}
	\caption{Distance to verify vs runtime: comparison between SAS and GS for different number of ReLUs open.}
	\label{fig55}
\end{figure}

>>>>

\begin{figure}[b!]
	\hspace*{-0.8cm}
	\includegraphics[scale=0.55]{CNN-B-ADV_layer7_comparison_image85_4methods.png}
	\caption{Distance to verify vs runtime: comparison between SAS, GS, full MILP and Huang's method for different number of ReLUs open.}
	\label{fig55}
\end{figure}
